04-1 - Refitted models

### 2023-01-26 scripts/r/04-1_refitted.Rmd
♻️ - add note about needing refitted models rds files

```{r}
#| label: get-divergent-transitions
# Function to add up all DTs from a model
get_dts <- function(df) {
  sum(subset(df, Parameter == "divergent__")$Value)
}

>>>>

For the following to run, it is necessary to have the individual refitted models in `data/analyses/models`.

```{r get-divergent-transitions}
# Function to add up all DTs from a model
get_dts <- function(df) {
  sum(subset(df, Parameter == "divergent__")$Value)
}
